\markedchapter{Doctor Who}{Verses from Doctor Who}\label{chapter-3}

\section{Section}\label{section-3.1}

\subsection{\texorpdfstring{It's art! A statement on modern society, `Oh
Ain't Modern Society
Awful?'!}{It's art! A statement on modern society, Oh Ain't Modern Society Awful?!}}\label{its-art-a-statement-on-modern-society-oh-aint-modern-society-awful}

They're not aliens, they're Earth\ldots{}liens! Father Christmas. Santa
Claus. Or as I've always known him: Jeff. You hate me; you want to kill
me! Well, go on! Kill me! KILL ME! I'm nobody's taxi service; I'm not
gonna be there to catch you every time you feel like jumping out of a
spaceship. You know how I sometimes have really brilliant ideas? Aw,
you're all Mr. \textbf{Grumpy Face today.} \emph{Sorry, checking all the
water in this area; there's an escaped fish.} I'm nobody's taxi service;
I'm not gonna be there to catch you every time you feel like jumping out
of a spaceship .

\input{figures/texs/fig:c3.tex}

\subsubsection{\texorpdfstring{I'm the Doctor, I'm worse than everyone's
aunt. \emph{catches himself} And that is not how I'm introducing
myself.}{I'm the Doctor, I'm worse than everyone's aunt. catches himself And that is not how I'm introducing myself.}}\label{im-the-doctor-im-worse-than-everyones-aunt.-catches-himself-and-that-is-not-how-im-introducing-myself.}

You know when grown-ups tell you `everything's going to be fine' and you
think they're probably lying to make you feel better? I hate yogurt.
It's just stuff with bits in. No, I'll fix it. I'm good at fixing rot.
Call me the Rotmeister. No, I'm the Doctor. Don't call me the
Rotmeister. No\ldots{} It's a thing; it's like a plan, but with more
greatness. Sorry, checking all the water in this area; there's an
escaped fish. Did I mention we have comfy chairs? \#\#\#\#\#They're not
aliens, they're Earth\ldots{}liens!\newline
You know when grown-ups tell you `everything's going to be fine' and you
think they're probably lying to make you feel better? All I've got to do
is pass as an ordinary human being. Simple. What could possibly go
wrong? I'm the Doctor. Well, they call me the Doctor. I don't know why.
I call me the Doctor too. I still don't know why. Father Christmas.
Santa Claus. Or as I've always known him: Jeff. \emph{Insistently} Bow
ties are cool! Come on Amy, I'm a normal bloke, tell me what normal
blokes do! You hit me with a cricket bat. Stop talking, brain thinking.
Hush. You know how I sometimes have really brilliant ideas? Saving the
world with meals on wheels. Annihilate? No. No violence. I won't stand
for it. Not now, not ever, do you understand me?! I'm the Doctor, the
Oncoming Storm - and you basically meant beat them in a football match,
didn't you? Stop talking, brain thinking. Hush. No\ldots{} It's a thing;
it's like a plan, but with more greatness. No, I'll fix it. I'm good at
fixing rot. Call me the Rotmeister. No, I'm the Doctor. Don't call me
the Rotmeister. It's art! A statement on modern society, `Oh Ain't
Modern Society Awful?'! You know when grown-ups tell you `everything's
going to be fine' and you think they're probably lying to make you feel
better? I'm the Doctor, I'm worse than everyone's aunt. \emph{catches
himself} And that is not how I'm introducing myself. Stop talking, brain
thinking. Hush. No, I'll fix it. I'm good at fixing rot. Call me the
Rotmeister. No, I'm the Doctor. Don't call me the Rotmeister. You hit me
with a cricket bat. The way I see it, every life is a pile of good
things and bad things.\ldots{}hey.\ldots{}the good things don't always
soften the bad things; but vice-versa the bad things don't necessarily
spoil the good things and make them unimportant. No\ldots{} It's a
thing; it's like a plan, but with more greatness. It's a fez. I wear a
fez now. Fezes are cool. Heh-haa! Super squeaky bum time! Sorry,
checking all the water in this area; there's an escaped fish. The way I
see it, every life is a pile of good things and bad
things.\ldots{}hey.\ldots{}the good things don't always soften the bad
things; but vice-versa the bad things don't necessarily spoil the good
things and make them unimportant. You know how I sometimes have really
brilliant ideas? The way I see it, every life is a pile of good things
and bad things.\ldots{}hey.\ldots{}the good things don't always soften
the bad things; but vice-versa the bad things don't necessarily spoil
the good things and make them unimportant. They're not aliens, they're
Earth\ldots{}liens! Sorry, checking all the water in this area; there's
an escaped fish. I'm the Doctor, I'm worse than everyone's aunt.
\emph{catches himself} And that is not how I'm introducing myself. I am
the Doctor, and you are the Daleks! You hit me with a cricket bat. The
way I see it, every life is a pile of good things and bad
things.\ldots{}hey.\ldots{}the good things don't always soften the bad
things; but vice-versa the bad things don't necessarily spoil the good
things and make them unimportant. You've swallowed a planet! I am the
Doctor, and you are the Daleks! Annihilate? No. No violence. I won't
stand for it. Not now, not ever, do you understand me?! I'm the Doctor,
the Oncoming Storm - and you basically meant beat them in a football
match, didn't you?

\section{Section}\label{section-3.2}

\subsection{The way I see it, every life is a pile of good things and
bad things.\ldots{}hey.\ldots{}the good things don't always soften the
bad things; but vice-versa the bad things don't necessarily spoil the
good things and make them
unimportant.}\label{the-way-i-see-it-every-life-is-a-pile-of-good-things-and-bad-things.hey.the-good-things-dont-always-soften-the-bad-things-but-vice-versa-the-bad-things-dont-necessarily-spoil-the-good-things-and-make-them-unimportant.}

Saving the world with meals on wheels. No\ldots{} It's a thing; it's
like a plan, but with more greatness. They're not aliens, they're
Earth\ldots{}liens! The way I see it, every life is a pile of good
things and bad things.\ldots{}hey.\ldots{}the good things don't always
soften the bad things; but vice-versa the bad things don't necessarily
spoil the good things and make them unimportant. I'm the Doctor, I'm
worse than everyone's aunt. \emph{catches himself} And that is not how
I'm introducing myself. I am the Doctor, and you are the Daleks!
Heh-haa! \textbf{Super squeaky bum time!} \emph{Aw, you're all Mr.}
Grumpy Face today. \#\#\#\# No, I'll fix it. I'm good at fixing rot.
Call me the Rotmeister. No, I'm the Doctor. Don't call me the
Rotmeister. I'm the Doctor. Well, they call me the Doctor. I don't know
why. I call me the Doctor too. I still don't know why. Annihilate? No.
No violence. I won't stand for it. Not now, not ever, do you understand
me?! I'm the Doctor, the Oncoming Storm - and you basically meant beat
them in a football match, didn't you? I hate yogurt. It's just stuff
with bits in. I'm the Doctor, I'm worse than everyone's aunt.
\emph{catches himself} And that is not how I'm introducing myself. It's
a fez. I wear a fez now. Fezes are cool. \textbf{You hate me; you want
to kill me! Well, go on! Kill me! KILL ME!} Saving the world with meals
on wheels. You know how I sometimes have really brilliant ideas? You
hate me; you want to kill me! Well, go on! Kill me! KILL ME! No\ldots{}
It's a thing; it's like a plan, but with more greatness. No\ldots{} It's
a thing; it's like a plan, but with more greatness. You know how I
sometimes have really brilliant ideas? It's art! A statement on modern
society, `Oh Ain't Modern Society Awful?'! Heh-haa! Super squeaky bum
time! You've swallowed a planet! I'm the Doctor. Well, they call me the
Doctor. I don't know why. I call me the Doctor too. I still don't know
why. No\ldots{} It's a thing; it's like a plan, but with more greatness.
You've swallowed a planet! Heh-haa! Super squeaky bum time! I'm the
Doctor, I'm worse than everyone's aunt. \emph{catches himself} And that
is not how I'm introducing myself. You know when grown-ups tell you
`everything's going to be fine' and you think they're probably lying to
make you feel better? All I've got to do is pass as an ordinary human
being. Simple. What could possibly go wrong? You know how I sometimes
have really brilliant ideas? You've swallowed a planet! I'm nobody's
taxi service; I'm not gonna be there to catch you every time you feel
like jumping out of a spaceship. Saving the world with meals on wheels.
You know when grown-ups tell you `everything's going to be fine' and you
think they're probably lying to make you feel better? Did I mention we
have comfy chairs? No\ldots{} It's a thing; it's like a plan, but with
more greatness. Stop talking, brain thinking. Hush. Sorry, checking all
the water in this area; there's an escaped fish. Saving the world with
meals on wheels. The way I see it, every life is a pile of good things
and bad things.\ldots{}hey.\ldots{}the good things don't always soften
the bad things; but vice-versa the bad things don't necessarily spoil
the good things and make them unimportant. Annihilate? No. No violence.
I won't stand for it. Not now, not ever, do you understand me?! I'm the
Doctor, the Oncoming Storm - and you basically meant beat them in a
football match, didn't you? You've swallowed a planet! You know how I
sometimes have really brilliant ideas? You hate me; you want to kill me!
Well, go on! Kill me! KILL ME! Did I mention we have comfy chairs? Aw,
you're all Mr.~Grumpy Face today. I am the Doctor, and you are the
Daleks! I hate yogurt. It's just stuff with bits in. It's a fez. I wear
a fez now. Fezes are cool. You've swallowed a planet! You hit me with a
cricket bat. Aw, you're all Mr.~Grumpy Face today. You hit me with a
cricket bat. All I've got to do is pass as an ordinary human being.
Simple. What could possibly go wrong? Aw, you're all Mr.~Grumpy Face
today. I am the Doctor, and you are the Daleks! Saving the world with
meals on wheels. You know how I sometimes have really brilliant ideas?
I'm nobody's taxi service; I'm not gonna be there to catch you every
time you feel like jumping out of a spaceship. I hate yogurt. It's just
stuff with bits in. No\ldots{} It's a thing; it's like a plan, but with
more greatness. I hate yogurt. It's just stuff with bits in. They're not
aliens, they're Earth\ldots{}liens!


\input{helpers/bib}
