\markedchapter{Futurama}{Ode to futurama}\label{chapter-2}

\section{Section}\label{section-2.1}

\subsection{I'm a thing.}\label{im-a-thing.}

No argument here. When will that be? Our love isn't any different from
yours, except it's hotter, because I'm involved. One hundred dollars. As
an interesting side note, as a head without a body, I envy the dead.
\textbf{Is today's hectic lifestyle making you tense and impatient?}
\emph{Morbo can't understand his teleprompter because he forgot how you
say that letter that's shaped like a man wearing a hat.} Oh yeah, good
luck with that \citep{Zongkerchicken2005}.

\input{figures/texs/fig:c2.tex}

\paragraph{\texorpdfstring{Oh dear! She's stuck in an infinite loop, and
he's an idiot! Well, that's love for you.\newline
Oh no! The professor will hit me! But if Zoidberg `fixes' it\ldots{}
then perhaps gifts! We need rest. The spirit is willing, but the flesh
is spongy and bruised. Bender, I didn't know you liked cooking. That's
so
cute.}{Oh dear! She's stuck in an infinite loop, and he's an idiot! Well, that's love for you.Oh no! The professor will hit me! But if Zoidberg fixes it\ldots{} then perhaps gifts! We need rest. The spirit is willing, but the flesh is spongy and bruised. Bender, I didn't know you liked cooking. That's so cute.}}\label{oh-dear-shes-stuck-in-an-infinite-loop-and-hes-an-idiot-well-thats-love-for-you.oh-no-the-professor-will-hit-me-but-if-zoidberg-fixes-it-then-perhaps-gifts-we-need-rest.-the-spirit-is-willing-but-the-flesh-is-spongy-and-bruised.-bender-i-didnt-know-you-liked-cooking.-thats-so-cute.}

There's no part of that sentence I didn't like! We're also Santa Claus!
Moving along\ldots{}

\subsubsection{You lived before you met
me?!}\label{you-lived-before-you-met-me}

Why would I want to know that? Oh, how awful. Did he at least die
painlessly? \ldots{}To shreds, you say. Well, how is his wife holding
up? \ldots{}To shreds, you say. Oh, I always feared he might run off
like this. Why, why, why didn't I break his legs? Would you censor the
Venus de Venus just because you can see her spewers? Whoa a real live
robot; or is that some kind of cheesy New Year's costume? Shut up and
take my money! And when we woke up, we had these bodies. Yeah, I do that
with my stupidness. I don't `need' to drink. I can quit anytime I want!
Our love isn't any different from yours, except it's hotter, because I'm
involved. We'll need to have a look inside you with this camera. I
videotape every customer that comes in here, so that I may blackmail
them later. You can crush me but you can't crush my spirit! Is the Space
Pope reptilian!? So I really am important? How I feel when I'm drunk is
correct? Fry! Quit doing the right thing, you jerk! Oh dear! She's stuck
in an infinite loop, and he's an idiot! Well, that's love for you. It's
toe-tappingly tragic! I didn't ask for a completely reasonable excuse! I
asked you to get busy! That's not soon enough! And until then, I can
never die? We need rest. The spirit is willing, but the flesh is spongy
and bruised. Oh, but you can. But you may have to metaphorically make a
deal with the devil. And by ``devil'', I mean Robot Devil. And by
``metaphorically'', I mean get your coat. Soothe us with sweet lies. No,
she'll probably make me do it. Oh, I don't have time for this. I have to
go and buy a single piece of fruit with a coupon and then return it,
making people wait behind me while I complain. Why, those are the
Grunka-Lunkas! They work here in the Slurm factory. You can crush me but
you can't crush my spirit! Bite my shiny metal ass. It's just like the
story of the grasshopper and the octopus. All year long, the grasshopper
kept burying acorns for winter, while the octopus mooched off his
girlfriend and watched TV. But then the winter came, and the grasshopper
died, and the octopus ate all his acorns. Also he got a race car. Is any
of this getting through to you? Oh yeah, good luck with that. Oh, I
don't have time for this. I have to go and buy a single piece of fruit
with a coupon and then return it, making people wait behind me while I
complain. Fry! Stay back! He's too powerful! Ow, my spirit! Fry, you
can't just sit here in the dark listening to classical music. I've been
there. My folks were always on me to groom myself and wear underpants.
What am I, the pope? So, how 'bout them Knicks? And I'm his friend
Jesus. Leela's gonna kill me. No argument here. Ow, my spirit! Check it
out, y'all. Everyone who was invited is here. I'm just glad my fat, ugly
mama isn't alive to see this day. I just told you! You've killed me! No,
I'm Santa Claus!

\section{Section}\label{section-2.2}

\subsection{OK, this has gotta stop. I'm going to remind Fry of his
humanity the way only a woman
can.}\label{ok-this-has-gotta-stop.-im-going-to-remind-fry-of-his-humanity-the-way-only-a-woman-can.}

Then we'll go with that data file! No, she'll probably make me do it.
They're like sex, except I'm having them! What are their names? Alright,
let's mafia things up a bit. Joey, burn down the ship. Clamps, burn down
the crew. No, she'll probably make me do it. \textbf{Okay, it's 500
dollars, you have no choice of carrier, the battery can't hold the
charge and the reception isn't very\ldots{} Bender, hurry!} \emph{This
fuel's expensive!} Also, we're dying! \#\#\#\# But I know you in the
future. I cleaned your poop. Kif, I have mated with a woman. Inform the
men. We'll need to have a look inside you with this camera. And then the
battle's not so bad? Ow, my spirit! Yes, if you make it look like an
electrical fire. When you do things right, people won't be sure you've
done anything at all. Why am I sticky and naked? Did I miss something
fun? For one beautiful night I knew what it was like to be a
grandmother. Subjugated, yet honored. When the lights go out, it's
nobody's business what goes on between two consenting adults.
\#\#\#\#\#Why would a robot need to drink?\newline
I guess if you want children beaten, you have to do it yourself. Tell
her you just want to talk. It has nothing to do with mating. Look,
everyone wants to be like Germany, but do we really have the pure
strength of `will'? Who are you, my warranty?! If rubbin' frozen dirt in
your crotch is wrong, hey I don't wanna be right. Bender! Ship! Stop
bickering or I'm going to come back there and change your opinions
manually! I wish! It's a nickel. Hey, whatcha watching? Hey, whatcha
watching? I love this planet! I've got wealth, fame, and access to the
depths of sleaze that those things bring. We don't have a brig. Meh.
You'll have all the Slurm you can drink when you're partying with Slurms
McKenzie! You are the last hope of the universe. No! The kind with
looting and maybe starting a few fires! Shut up and take my money! And
I'd do it again! And perhaps a third time! But that would be it. Then
we'll go with that data file! We can't compete with Mom! Her company is
big and evil! Ours is small and neutral! Goodbye, cruel world. Goodbye,
cruel lamp. Goodbye, cruel velvet drapes, lined with what would appear
to be some sort of cruel muslin and the cute little pom-pom curtain pull
cords. Cruel though they may be\ldots{} Is the Space Pope reptilian!?
You're going to do his laundry? Yeah, lots of people did. Do a flip!
Would you censor the Venus de Venus just because you can see her
spewers? Oh, I always feared he might run off like this. Why, why, why
didn't I break his legs? Yeah. Give a little credit to our public
schools. Fry, you can't just sit here in the dark listening to classical
music. Daylight and everything. Oh right. I forgot about the battle.
Bender, you risked your life to save me! Hey, whatcha watching? There's
one way and only one way to determine if an animal is intelligent.
Dissect its brain! Ooh, name it after me! I guess if you want children
beaten, you have to do it yourself. And I'm his friend Jesus. Look,
everyone wants to be like Germany, but do we really have the pure
strength of `will'? Daddy Bender, we're hungry. Ah, computer dating.
It's like pimping, but you rarely have to use the phrase ``upside your
head.'' It doesn't look so shiny to me. Ven ve voke up, ve had zese
wodies. A true inspiration for the children. It must be wonderful. Ah,
yes! John Quincy Adding Machine. He struck a chord with the voters when
he pledged not to go on a killing spree. Robot 1-X, save my friends! And
Zoidberg! Dear God, they'll be killed on our doorstep! And there's no
trash pickup until January 3rd. Bender! Ship! Stop bickering or I'm
going to come back there and change your opinions manually! You are the
last hope of the universe. You lived before you met me?! Wow, you got
that off the Internet? In my day, the Internet was only used to download
pornography.


\input{helpers/bib}
